Effects of CHILDREN's programs

### 2020-02-22 paper.Rnw
minor updates

% To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
\section{Outline}
Descriptive statistics\\
- dynamics of selected outcomes\\
- dynamics of real subsidy per institution\\
- dynamics of real total subsidy\\
(- dynamics of real subsidy per individual)\\
(- which variables have largest variance; also relevant for variable selection)\\

@@

Questions:\\
- effect of healthy meals (DGE criterion) on healthy characteristics\\
- effect of real meals subsidy on number of meals\\
- effect of real trips subsidy on number of trips\\
- effect of real meals subsidy on self-worth and day-to-day skills\\

>>>>

% To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
\section{Outline}
Descriptive statistics\\
dynamics of\\ 
(- number of organizations)\\
(- number of beneficiaries)\\
- selected ordinal outcomes, stacked\\
- real total subsidy\\
- real median subsidy per institution\\
- real median subsidy per beneficiary\\
(- which variables have largest variance; also relevant for variable selection)\\

@@

Questions:\\
effect of\\
- healthy meals (DGE criterion) on healthy characteristics\\
- real meals subsidy on number of meals\\
- real trips subsidy on number of trips\\
- real meals subsidy on self-worth and day-to-day skills\\
- real trips subsidy on self-worth and day-to-day skills\\
